Legends for supplementary material

### 2020-01-23 Manuscript/Supplementary/supplementary_legends.Rmd
edits

**Supplementary Table 3.** Domain data and class imbalance summaries across resolutions for GM12878.

@@

>>>>

**Supplementary Table 3.** Domain data and class imbalance summaries across resolutions for K562.

@@

**Supplementary Figure 2. Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance for K562.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics. Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.

**Supplementary Figure 3. The proportional importance of optimally built random forest models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the computational framework (SMOTE re-sampling; with distance-type predictors), for each resolution on (A) GM12878 and (B) K562. Proportions are grouped by the class of cell line specific genomic elements in the feature space including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
